Forward Modeling Galaxy Size in a Cosmological Context

### 2017-10-04 paper/galsize_paper.tex
Finshed satellite evolution implications section

Points to address:
\ben
\item $\rhalf$ is set at $\zpeak.$ Stripping appears to be statistically unimportant.
\item The $\rhalf-\rspeak$ correlation implies a very long timeline for co-evolution, since $R_{\rm s}$ is largely frozen in at the time
\een

>>>>

Explanations for differences between the sizes of centrals and satellites fall into two categories, depending on whether or not the processes involved are specific to post-infall physics. One obvious possibility that could lead to satellites being smaller than centrals of the same $\mhalo$ is tidal stripping: satellite $\mstar$ could decrease after infall, reducing the size of the galaxy. We have quantitatively tested this possibility with the $\mstar-$stripping model described in \S\ref{subsubsec:strippingmodel}. Comparing the clustering ratios of the ``$\rvir-$only" and ``$\rvir+$stripping" models in Figure \ref{fig:strippingorphans}, we find that the impact of physically motivated levels of satellite mass loss cannot explain the $\rhalf-$dependent clustering seen in SDSS. As an additional test, we reach the same conclusion when implementing an even more extreme $\mstar-$stripping model in which stellar mass loss is linearly proportional to halo mass loss \citep[][Model 1]{watson_etal12}.

Both the $\rvir-$only model and the co-evolution model (see sections \S\ref{subsubsec:rvirmodel} and \S\ref{subsubsec:coevolutionmodel}, respectively) represent explanations falling into the second category, in which centrals and satellites of the same $\mhalo$ have different sizes due to their different evolutionary paths {\em prior} to satellite infall. For these models the story is very different: the influence of pre-infall co-evolution has a dramatic impact on $\rhalf-$clustering ratios, with a scale- and $\mstar-$dependence that closely resembles the SDSS signal. Quantitative constraints on the true level of this co-evolution effect will be a natural outcome of the program described in \S\ref{subsec:future}, but it is already clear that the long term co-evolution of galaxy and halo profiles should be considered a critical ingredient to models for the distribution of galaxy sizes across the cosmic web.
